The importance of measurement uncertainty in ecological management

### 2018-01-29 manuscripts/manuscript.Rmd
draft

bibliography: citations.bib
csl: the-american-naturalist.csl
output: rticles::elsevier_article
layout: 3p # review # review = doublespace, 3p = singlespace, 5p = two-column

@@

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7,  dev="cairo_pdf")
library(tidyverse)
library(gridExtra)
```

>>>>

bibliography: citations.bib
#journal: "The American Naturalist"
date: "`r Sys.Date()`"
csl: the-american-naturalist.csl
output: rticles::elsevier_article
layout: 3p # review # review = doublespace, 3p = singlespace, 5p = two-column
header-includes: |
        \journal{The American Naturalist}

@@

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7,  dev="cairo_pdf", cache = TRUE)
library(tidyverse)
library(gridExtra)
```
